Introducing Distributed Dynamic Data-intensive (D3) Science: Understanding Applications and Infrastructure

### 2016-09-06 rebuttal.tex

\textbf{Response:} We've reworked the first paragraph of Section 1 to address this.

\item \emph{``In this paper, we use locally distributed to indicate that data/compute resides on multiple nodes within one data center. Geographically distributed describes the distribution of data and/or compute across multiple data centers'' Given the above, I think it would be better in this definition to also separate out data creation location from compute location. Intro: Define precisely what is meant by ``dynamic,'' here as it is key to the paper but isn't well defined in Section 1 (see recommendation above to fix this by moving definitions from Section 3).}

\textbf{Response:}

We have added a summary description of wha t we mean by distributed and dynamic at the start of Section 2 to reflect the fact that definition of the terminology arose and was refined by the discussions at the workshops, and the analysis of the application scenarios presented.
In addition, recognizing that the two reviewers have different styles of reading
and different areas of expertise (as do we as authors), we have added a paragraph at the end
of Section 1 to explain how different types of readers might want to approach this paper.  We do
not believe that there is one single way of organizing it that would satisfy all readers.  We have also
added a longer description of each section at this same place.  Also, see our response to point 10 below.
